\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{iftex}

\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{mathptmx}
\else
  \usepackage{fontspec}
  \setmainfont{Times New Roman}
\fi

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlength{\emergencystretch}{2em}
\linespread{1.03}
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=3pt,
  topsep=4pt,
  partopsep=0pt,
  parsep=0pt
}

\newcommand{\resumesection}[1]{
  \vspace{10pt}
  {\normalsize\bfseries\MakeUppercase{#1}\par}
  \vspace{3pt}
  \hrule
  \vspace{7pt}
}

\newcommand{\companyheading}[2]{
  \noindent\textbf{#1}\hfill\textbf{#2}\par
}

\newcommand{\roleheading}[2]{
  \noindent\textit{#1}\hfill #2\par
}

\newcommand{\companysummary}[1]{
  {\small #1\par}
  \vspace{2pt}
}

\newcommand{\entryspace}{
  \vspace{6pt}
}

\begin{document}

{\LARGE \textbf{Jason (Yue) Zhang}\par}
\vspace{4pt}
{\normalsize
\href{mailto:zhangyue1208@gmail.com}{zhangyue1208@gmail.com}
\;|\;
(858) 349-8335
\;|\;
San Francisco, California\par
}

\resumesection{Work Experience}

\companyheading{Propel Code}{Aug. 2025 -- Present}
\roleheading{Founding Software Engineer}{San Francisco, CA}
\companysummary{Propel Code builds an LLM-based code review product for engineering teams to improve code quality and review velocity.}
\begin{itemize}\small
  \item Built TypeScript, Node/Express, React, GraphQL, and PostgreSQL product surfaces and backend services for an LLM-based code review product that has reviewed 200K PRs.
  \item Pioneered an evaluation system that improved review accuracy and enabled faster iteration on prompts, models, and product behavior.
  \item Led migration of core review workflows from River to Temporal, improving reliability and making the product more resilient at scale.
  \item Owned AWS infrastructure managed with Terraform, shipping changes across backend services, product surfaces, and workflow infrastructure.
\end{itemize}
\entryspace
\normalsize

\companyheading{Nextdoor}{Jan. 2023 -- Aug. 2025}
\roleheading{Staff Software Engineer}{San Francisco, CA}
\companysummary{Nextdoor is a hyperlocal social networking platform that fosters communication between neighbors and promotes local businesses within neighborhoods.}
\begin{itemize}\small
  \item Led technical direction for Ads Measurement and Nextdoor Ads Manager, owning architecture, roadmap, and execution across attribution, identity, and events systems.
  \item Revamped the Conversion Attribution Platform and Ads Manager workflows with TypeScript, React, GraphQL, Node/Express, and PostgreSQL, doubling adoption while improving attribution accuracy, usability, and advertiser trust.
  \item Led user identification and events-management initiatives that increased identification rate by 50\%, supported 1K advertisers during platform migration, and unlocked 2--5\% projected annual revenue impact.
  \item Tech-led an Ads Reporting rebuild with Databricks, leading 3 engineers to launch a platform supporting 100+ report types and cutting support SLA from 5 to 2 business days.
  \item Mentored 20+ engineers and partnered closely with PM, Design, Sales, GTM, and Data Science to prioritize and ship roadmap investments.
\end{itemize}
\entryspace
\normalsize

\companyheading{Twitter}{Jul. 2018 -- Nov. 2022}
\companysummary{Twitter is a leading social media platform with billions in annual revenue and millions of active users, facilitating global real-time communication.}

\roleheading{Senior Software Engineer -- Signal Acquisition | Jul. 2022 -- Nov. 2022}{San Francisco, CA}
\begin{itemize}\small
  \item Led an offline signal acquisition and ML feature conversion platform that improved pConv precision by 2\%.
  \item Architected a JavaScript/Webpack pixel-tracking API that consolidated legacy integrations, reduced technical debt, and simplified future product development.
  \item Saved \$1M/year in infrastructure through data-driven debugging, targeted testing, and predictive analysis while improving team data governance.
  \item Mentored newer engineers through technical presentations and context sharing on complex systems.
\end{itemize}
\entryspace
\normalsize

\roleheading{Software Engineer -- SMB | Jul. 2018 -- Jul. 2022}{San Francisco, CA}
\begin{itemize}\small
  \item Led development of a lead generation solution that collected 100K sales prospects with MapReduce, Thrift, and Vertica, improving sales outreach effectiveness.
  \item Designed and developed an ML feature preparation pipeline that integrated media classification annotation into business identification models and improved model accuracy by 5\%.
  \item Developed internal product tools that automated daily operations for the Marketing team.
  \item Advocated for and onboarded the team to BigQuery, helping migrate Python pipeline code and modernize data workflows.
\end{itemize}
\entryspace
\normalsize

\resumesection{Education}
\companyheading{University of California, San Diego}{Mar. 2013}
\textit{Bachelor of Science, Computer Science and Engineering}\par

\resumesection{Technical Skills}
{\small
\textbf{Languages:} TypeScript, JavaScript, Go, Python, SQL \par
\textbf{Product \& Backend:} React, Node.js, Express, GraphQL, PostgreSQL \par
\textbf{Cloud, Data \& Systems:} AWS, Terraform, Databricks, BigQuery, Distributed Systems, AI Evaluation, LLM Applications \par
}

\end{document}
